Game Theory based Peer Grading Mechanisms for MOOCs

### 2015-01-08 Paper.tex
More small fixes, and copyright

\toappear{Pending copyright...}

@@

Where $w_i$ is the work done, or number of assignments graded, by the $i$th person, $g_i$ is the grade given by student grader on the $i$th assignment, and $o_i$ is the grade that would have been given by the professor on the $i$th assignment. $H$ is the happiness function defined in section~\ref{sec:modelandassumptions}.

>>>>

\toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is  granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\
{\emph{L@S'15}}, March 14-15, 2015, Vancouver, Canada. \\
Copyright \copyright~2015 ACM ISBN/15/03...\$15.00. \\
DOI string from ACM form confirmation}

@@

Where $w_i$ is the work done or number of assignments graded by the $i$th person, $g_i$ is the grade given by student grader on the $i$th assignment, and $o_i$ is the grade that would have been given by the professor on the $i$th assignment. $H$ is the happiness function defined in section~\ref{sec:modelandassumptions}.
